A Comparison of Use-Case Based and Checklist- Based Reading: A Controlled Experiment

### 2015-03-18 rmtw/a6/latex8.tex
Added purpose + notes to A6

\section{Introduction}
%Literature intro
%A bit unclear what to write here - check with Branson

\subsection{Problem Statement}

\subsection{Purpose Statement}

\subsection{Research Questions}

>>>>

\section{Introduction}

\subsection{Introduction to Topics}

\subsubsection{API Design}
Explain what APIs are. 
Explain how and that APIs change.

\subsubsection{Software Evolution}
Introduce software evolution. 
Link this paragraph nicely to the previous one.

\subsection{Problem Statement}
Talk about how changing APIs is costly and how it might be hard to avoid changes since a lot of how good an API is depends on the user of the API. (Maybe even a reference to someone saying that user testing is expensive).

\subsection{Gap in the Literature}
API change + software evolution.

\subsection{Purpose of the Study}
The purpose of the study is to find the motives behind modifications of APIs. This would be of value to academia, since APIs in the context of software evolution are relatively unexplored (!!!cite). The value of such a study is especially high since modifying APIs has a large impact on the API user {!!!cite, google talk}. This study is also of value for companies who wish to improve their APIs. By exploring why APIs change it can help companies in API design through highlighting areas where extra effort could be put in during the development (or improvement) of APIs.

\subsection{Research Questions}
RQ1: What drives API evolution? 
SRQ1: To what extent can we reverse engineer API change decisions?
SRQ2: Are changes/improvements to APIs made for good reasons? (Compare why the changes were made to best practises for why you should change APIs)
